This thesis has been made possible due to the contributions of many people.
First and foremost, I would like to express the sincerest gratitude to my advisor, Associate Professor Hari Sundaram, for his constant support and guidance.
My most prominent learning from his mentorship is his unique problem-solving skills and critical thinking.
His attention to detail, including presentation skills, has also improved clarity in my academic writing. With the independence afforded by him in my research, I was able to explore and work in diverse areas helping me become a more holistic researcher.

I also extend my heartfelt thanks to Assistant Professor Alexander Schwing for taking me under his wings and teaching me the ropes of deep learning. I appreciate him devoting so much time to mentor me even when our research interests did not align.
I thoroughly enjoyed working with him, and he is among the most optimistic and supportive people I know in academia.
Next, I would like to thank my committee members, Professor ChengXiang Zhai and Dr. Chris Brew, for their contributions to this thesis.
Prof. Zhai has taught me the importance of situating your research in the grand scheme of things. He has pushed me harder to think about the broader impact of my research that has dramatically improved the writing quality of this thesis. I also thank Dr. Brew for teaching me the importance of fundamental research and to being critical even of positive results.

I am also grateful to Assistant Professor Snigdha Chaturvedi and Dr. Susan Dumais for mentoring me in the initial years of my Ph.D. and providing an exemplar example of successful women researchers in the field. I feel fortunate to be advised by exceptional mentors in my career.
A big shout out to especially Professor Pankaj Jalote, Professor Ponnurangam Kumaraguru (PK), and Professor Mayank Vatsa at my undergraduate institution, Indraprastha Institute of Information Technology (IIIT-D), for igniting the flame of research curiosity in my formative years. My initial experiences during IIIT-D helped me appreciate the joys and importance of research and motivated me to pursue it as a full-time career.

Thanks also to my colleagues at Crowd Dynamics Lab for being my mentors, support system, and critiques of my research.
All my friends outside work also deserve a special mention for helping me maintain a semblance of a personal life beyond my research.

Finally, to my parents for believing in my dream and their continued love and support over the years. This acknowledgment will not be complete without mentioning my fianc\'e, Dr. Ketan Mittal. Thanks for being my pillar of strength and an ardent champion of my success throughout this time. I owe a great deal of this thesis to him.
