\chapter{Literature Review}
\label{sec:related}

Before delving into details of our proposed approach, we first discuss prior literature related to User Behavior Modeling in Online Social Networks, Academic Dataset and Recommender Systems. We also review text representation approaches used in Community Question Answering (CQA) forums and for short text in Twitter. We also briefly review recently proposed Graph convolution networks to model graph-structured data (used in our work) for these platforms.

\section{Online Social Networks}
There has been a lot of interest in the past on identifying and characterizing user behavior in online social networks (OSNs). \citet{Maia:2008} identified five distinct user behaviors of YouTube users based on their individual and social attributes. While \citet{Mamykina:2011} identified user roles based on just answer frequency in StackExchange. \citet{Adamic:2008} and \citet{Furtado:2013} worked on similar user behavioral studies on Yahoo Answers and Stack Overflow datasets, respectively. All these studies, however, ignore \emph{temporal changes} in the behavior and use engineered features for behavior modeling.

Some behavioral studies do model evolution of user activities in the platform too. \citet{Benevenuto:2009} learned a Markov model to examine transition behavior of users between different activities in Orkut in a static snapshot. \citet{Yang:2014} and \citet{Knab2003} proposed generative models that assigned each user action to a progression stage and classify event sequences simultaneously. They used their model to predict cancer symptoms, or products user would review in the future. However, the model did little to provide meaningful and interpretable stages and clusters. \citet{Angeletou:2011} constructed handcrafted rules to identify user roles and studied the change of user roles' composition in the community over time. Recently, \citet{Santos:2019} identified four distinct types of user activity pattern based on their activity frequency.

The Hidden Markov Model (HMM) has been widely used to model and cluster time sequences \citep{Smyth:1997, Bicego:2003, Coviello:2014} in the past. However, most of these models learn an HMM for each user sequence and then employ clustering algorithms to cluster the learned HMMs. These approaches are not scalable, and the clusters thus identified are not interpretable.

\section{Recommender Systems}
\input{social_related.tex}

\section{Scholarly Data}
Most of the work on user behavioral mining concerns career movement within academia. \citet{deville:2014} observed that transitions between academic institutions are influenced by career stage and geographical proximity. While \citet{clauset:2015} found that academic prestige correlates with higher productivity and better faculty placement. Recently, \citet{Danai:2018} studied career transitions across academia, government, and industry for Computer Science researchers. \citet{dashun:2013} proposed a statistical model to predict the most impactful paper, in terms of citations, of scientists across disciplines. They argued nonexistence of a universal pattern and showed that highest-impact work in a scientist's career is randomly distributed within her body of work.

Recent studies also looked at gender differences in funding patterns, productivity, and collaboration trends in academia \citep{Way:2016, Way:2017}. \citet{Way:2016} did not observe any significant difference across gender in hiring outcomes in academia. However, they showed that indirect gender differences exist in terms of productivity, postdoctoral training rates, and in career growth. Some earlier studies also reported gender differences in academia. \citet{Kahn:1993} identified gendered barriers in obtaining tenure for academics in economics, while \citet{Ward:2001} found gendered differences in pay related to publication record.

There also has been considerable interest in mining scholarly data produced by researchers (bibliographic data, researchers' usage of social media, etc.). Prior studies have looked at the evolution of research interests on a community level. \citet{liu2014chi} studied the evolution of research themes in articles published in CHI conference on Human Computer Interaction through co-word analysis. They highlighted specific topics as popular, core, or backbone research topics within the community. While \citet{Biryukov:2010} compared different scientific communities in DBLP dataset in terms of its interdisciplinary nature, publication rates, and collaboration trends. They also studied the variation of author's productivity with career length and observed that most of the authors have a short career spanning less than five years. \citet{Chakraborty:2018} studied trajectories of successful papers in computer science and physics by analyzing paper citation counts. They classified these trajectories into multiple categories including early riser, a late riser, steady riser, and steady dropper.

\section{Community Question Answering Forums}
\input{crowdqm-relatedwork5.tex}

\section{Twitter}
\input{hate_RelatedWork}

\noindent
\section{Graph Convolution Networks}
More recently, Graph Convolution Networks (GCNs) have been proposed to learn embeddings for graph-structured data~\cite{Kipf:2016}. Graph Convolution can be applied in both spatial and spectral domains to compute node representations. The learned node representations are then used for various downstream tasks like node classification \cite{gcn}, link prediction \cite{relationalGCN}, multi-relational tasks \cite{rase} etc. Spatial approaches employ random walks or k-hop neighborhoods to compute node representations  \cite{DeepWalk, node2vec, Planetoid, LINE}. Pioneer works on graph convolution in the spectral domain use fast localized convolutions ~\cite{deferrard, duvenaund}. Recently proposed Graph Convolution Networks~\cite{gcn} outperforms spatial convolutions and are scalable to large graphs. Various extensions to the GCN model have been proposed for signed networks \cite{signedgcn}, inductive settings \cite{graphsage} and multiple relations \cite{DualGCN, relationalGCN} and evolution~\cite{dysat}. All of the GCN variants assume label sharing as they assume similarity between connected nodes.

In Recommender Systems, GCNs have been used to model the user-item interaction graph. GCMC~\cite{GCMC} extends GCN by training an auto-encoder framework on a  bipartite user-item interaction graph that performs differentiable message passing, aggregating data from a user's and an item's 'neighbors'. PinSage~\cite{PinSage} proposed a random walk based sampling of neighbors to scale GCNs to web scale graphs. \citet{fan2019} further extend these methods to incorporate information from a user's social connections.
Similarly, \citet{Diffnet} use graph neural networks to model diffusion of social influence in recommender systems.

However, these methods either do not take a user's social neighbors into account or operate on static features.  All these models also assign uniform weight to all their neighbors, which does not represent online social communities well. Typically in these communities, some friends are only superficially known while others are known personally for years. Thus, they exert a different degree of influence on a user's behavior. Graph Attention Networks~\cite{GAT} can capture the varying influence stengths as they learn attention weights between each pair of nodes in a static graph.
